---
title: "Untitled"
author: "Deirdre Lawless"
date: "26 October 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown




```{r }
library(ggplot2)
dbData <- read.csv("feedbackdb.csv",  header = TRUE)
gg <- ggplot(dbData, aes(x=dbData$Total))
gg <- gg + labs(x="Lab Test Total")
gg <- gg + geom_histogram(binwidth=4, colour="black", aes(y=..density.., fill=..count..))
gg <- gg + scale_fill_gradient("Count", low="#DCDCDC", high="#7C7C7C")
gg <- gg + stat_function(fun=dnorm, color="red",args=list(mean=mean(dbData$Total, na.rm=TRUE), sd=sd(dbData$Total, na.rm=TRUE)))
gg <- gg + stat_function(fun=dnorm, color="red",args=list(mean=mean(dbData$Total, na.rm=TRUE), sd=sd(dbData$Total, na.rm=TRUE)))
gg <- gg + stat_function(fun=dnorm, color="red",args=list(mean=mean(dbData$Total, na.rm=TRUE), sd=sd(dbData$Total, na.rm=TRUE)))
gg
```

```{r}
db228<-subset(dbData, Total=="DT228")
gg <- ggplot(db228, aes(x=db228$Total))
gg <- gg + labs(x="Lab Test Total (DT228)")
gg <- gg + geom_histogram(binwidth=4, colour="black", aes(y=..density.., fill=..count..))
gg <- gg + scale_fill_gradient("Count", low="#DCDCDC", high="#7C7C7C")
gg <- gg + stat_function(fun=dnorm, color="red",args=list(mean=mean(db228$Total, na.rm=TRUE), sd=sd(db228$Total, na.rm=TRUE)))
gg <- gg + stat_function(fun=dnorm, color="red",args=list(mean=mean(db228$Total na.rm=TRUE), sd=sd(db228$Total, na.rm=TRUE)))
gg <- gg + stat_function(fun=dnorm, color="red",args=list(mean=mean(db228$Total, na.rm=TRUE), sd=sd(db228$Total, na.rm=TRUE)))
gg